Replication Script to JSS Submission

### 2016-05-22 JSS-ggenealogy/ReplicationScript.Rnw
Retain necessary files

<<eval=TRUE>>=
rm(list=)
library("devtools")
load_all("ggenealogy")
library("ggenealogy")
data("sbGeneal")
str(sbGeneal)
@

@@

<<eval=TRUE>>=
plotPath(pathTN)
@

@@

<<eval=TRUE>>=
pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal)
plotPath(pathBZ, fontFace = 2)
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:3, pathEdgeCol = "red", nodeSize = 2.5, pathNodeSize = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 12), axis.title = ggplot2::element_text(size = 12))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, pathEdgeCol = "seagreen2", nodeSize = 1, pathNodeSize = 3)
@

@@

<<eval=TRUE>>=
plotAncDes("Lee", sbGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<eval=TRUE>>=
varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow", "Pella", "Tokyo", "Young", "Zane")
plotDegMatrix(varieties, sbIG, sbGeneal, "Variety", "Variety", "Degree") + ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") + ggplot2::theme(legend.title = ggplot2::element_text(size = 15), legend.text = ggplot2::element_text(size = 15))
@

@@

<<eval=TRUE>>=
plotAncDes("David Cox", statGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@

@@

<<eval=TRUE>>=
pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal, isDirected = FALSE)
plotPath(pathCB, fontFace = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 10), axis.title = ggplot2::element_text(size = 10)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200) + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray") + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@

@@

<<eval=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray", animate = TRUE)
@

>>>>

<<eval=TRUE>>=
rm(list=)
library("devtools")
load_all("SourceCode")
library("ggenealogy")
data("sbGeneal")
str(sbGeneal)
@

@@

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal)
plotPath(pathBZ, fontFace = 2)
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:3, pathEdgeCol = "red", nodeSize = 2.5, pathNodeSize = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 12), axis.title = ggplot2::element_text(size = 12))
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotPathOnAll(pathTN, sbGeneal, sbIG, binVector = 1:6, pathEdgeCol = "seagreen2", nodeSize = 1, pathNodeSize = 3)
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotAncDes("Lee", sbGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
varieties <- c("Brim", "Bedford", "Calland", "Dillon", "Hood", "Narow", "Pella", "Tokyo", "Young", "Zane")
plotDegMatrix(varieties, sbIG, sbGeneal, "Variety", "Variety", "Degree") + ggplot2::scale_fill_continuous(low = "white", high = "darkgreen") + ggplot2::theme(legend.title = ggplot2::element_text(size = 15), legend.text = ggplot2::element_text(size = 15))
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotAncDes("David Cox", statGeneal, mAnc = 6, mDes = 6, vCol = "blue")
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
pathCB <- getPath("David Cox", "Petra Buzkova", statIG, statGeneal, isDirected = FALSE)
plotPath(pathCB, fontFace = 4) + ggplot2::theme(axis.text = ggplot2::element_text(size = 10), axis.title = ggplot2::element_text(size = 10)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200) + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray") + ggplot2::theme(axis.text = ggplot2::element_text(size = 8), axis.title = ggplot2::element_text(size = 8)) + ggplot2::scale_x_continuous(expand = c(.1, .2))
@
\end{figure}

@@

\begin{figure}[H]
\centering
<<fig=TRUE, echo=TRUE>>=
plotPathOnAll(pathCB, statGeneal, statIG, binVector = 1:200, nodeSize = .5, pathNodeSize = 2.5, nodeCol = "darkgray", edgeCol = "lightgray", animate = TRUE)
@
\end{figure}
